**The Place of Interoception and Theory of Mind in Deception**

### 2021-11-11 3_ToM.Rmd
update script

plot_effect(model, var = "YONI_Total", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "YONI_Total", outcome = "RT")
```

@@

#### LIE Scale

```{r message=FALSE, warning=FALSE}
r <- get_correlation(var = "BES_")
r$plot
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "BES_Total", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "BES_Total", outcome = "RT")
```

>>>>

p_conf_yoni_total <- plot_effect(model, var = "YONI_Total", outcome = "Confidence")
# p_conf_yoni_total
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_yoni_total <- plot_effect(model, var = "YONI_Total", outcome = "RT")
# p_rt_yoni_total
```

### Cognitive Theory of Mind

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Cognitive) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_yoni_cognitive <- plot_effect(model, var = "YONI_Cognitive", outcome = "Confidence")
# p_conf_yoni_cognitive
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * YONI_Cognitive) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_yoni_cognitive <- plot_effect(model, var = "YONI_Cognitive", outcome = "RT")
# p_rt_yoni_cognitive
```

### Affective Theory of Mind

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Affective) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_yoni_affective <- plot_effect(model, var = "YONI_Affective", outcome = "Confidence")
# p_conf_yoni_affective
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * YONI_Affective) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_yoni_affective <- plot_effect(model, var = "YONI_Affective", outcome = "RT")
# p_rt_yoni_affective
```

### Physical Theory of Mind

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Physical) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_yoni_physical <- plot_effect(model, var = "YONI_Physical", outcome = "Confidence")
# p_conf_yoni_physical
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * YONI_Physical) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_yoni_physical <- plot_effect(model, var = "YONI_Physical", outcome = "RT")
# p_rt_yoni_physical
```

### Summary

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
p_conf_yoni_total / 
  p_conf_yoni_cognitive / 
  p_conf_yoni_affective / 
  p_conf_yoni_physical +
  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_yoni_total / 
  p_rt_yoni_cognitive / 
  p_rt_yoni_affective / 
  p_rt_yoni_physical +
  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
```

@@

@@

```{r message=FALSE, warning=FALSE}
p_conf_bes_total <- plot_effect(model, var = "BES_Total", outcome = "Confidence")
# p_conf_bes_total
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_bes_total <- plot_effect(model, var = "BES_Total", outcome = "RT")
# p_rt_bes_total
```

### Cognitive Empathy

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Cognitive) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_bes_cognitive <- plot_effect(model, var = "BES_Cognitive", outcome = "Confidence")
# p_conf_bes_cognitive
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * BES_Cognitive) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_bes_cognitive <- plot_effect(model, var = "BES_Cognitive", outcome = "RT")
# p_rt_bes_cognitive
```

### Affective Empathy

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Affective) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_bes_affective <- plot_effect(model, var = "BES_Affective", outcome = "Confidence")
# p_conf_bes_affective
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * BES_Affective) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_bes_affective <- plot_effect(model, var = "BES_Affective", outcome = "RT")
# p_rt_bes_affective
```

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
r <- get_correlation(var = "BES_")
r$plot
```

### Summary

```{r message=FALSE, warning=FALSE}
p_conf_bes_total / 
  p_conf_bes_cognitive / 
  p_conf_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_bes_total / 
  p_rt_bes_cognitive / 
  p_rt_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
```

### 2021-11-11 4_Intero.Rmd
update script

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Accuracy", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Accuracy", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Confidence", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Confidence", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Awareness", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "HCT_Awareness", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_Total", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_Total", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_Noticing", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_Noticing", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_NotDistracting", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
plot_effect(model, var = "MAIA_NotDistracting", outcome = "RT")
```

>>>>

```{r message=FALSE, warning=FALSE}
p_conf_hct_accuracy <- plot_effect(model, var = "HCT_Accuracy", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_hct_accuracy <- plot_effect(model, var = "HCT_Accuracy", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_hct_confidence <- plot_effect(model, var = "HCT_Confidence", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_hct_confidence <- plot_effect(model, var = "HCT_Confidence", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_hct_awareness <- plot_effect(model, var = "HCT_Awareness", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_hct_awareness <- plot_effect(model, var = "HCT_Awareness", outcome = "RT")
```

### Summary

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
p_conf_hct_accuracy / 
  p_conf_hct_confidence / 
  p_conf_hct_awareness +
  patchwork::plot_annotation(title = "Interoception", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_hct_accuracy / 
  p_rt_hct_confidence / 
  p_rt_hct_awareness +
  patchwork::plot_annotation(title = "Interoception", theme = theme(plot.title = element_text(hjust = 0.5)))
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_total <- plot_effect(model, var = "MAIA_Total", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_total <- plot_effect(model, var = "MAIA_Total", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_noticing <- plot_effect(model, var = "MAIA_Noticing", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_noticing <- plot_effect(model, var = "MAIA_Noticing", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_notdistracting <- plot_effect(model, var = "MAIA_NotDistracting", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_notdistracting <- plot_effect(model, var = "MAIA_NotDistracting", outcome = "RT")
```

### Body Listening

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * MAIA_BodyListening) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

```{r message=FALSE, warning=FALSE}
p_conf_maia_bodylistening <- plot_effect(model, var = "MAIA_BodyListening", outcome = "Confidence")
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * MAIA_BodyListening) + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
p_rt_maia_bodylistening <- plot_effect(model, var = "MAIA_BodyListening", outcome = "RT")
```

### Summary

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
p_conf_maia_total / 
  p_conf_maia_noticing / 
  p_conf_maia_notdistracting / 
  p_conf_maia_bodylistening +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_maia_total / 
  p_rt_maia_noticing / 
  p_rt_maia_notdistracting / 
  p_rt_maia_bodylistening +
  patchwork::plot_annotation(title = "Interoception (MAIA)", theme = theme(plot.title = element_text(hjust = 0.5)))
```

### 2021-11-11 index.Rmd
update script

---
title: '**The Place of Interoception and Theory of Mind in Deception**'
subtitle: A Subtitle
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: no
    df_print: kable
    code_folding: hide
    code_download: yes
  word_document:
    reference_docx: utils/Template_Word.docx
    highlight: pygments
    toc: no
    toc_depth: 3
    df_print: kable
    number_sections: yes
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '2'
    latex_engine: xelatex
editor_options:
  chunk_output_type: console
bibliography: utils/bibliography.bib
csl: utils/apa.csl
---

@@

<!-- # Manipulation Checks -->

<!-- ```{r child='2_ManipulationChecks.Rmd'} -->
<!-- ``` -->

<!-- # Theory of Mind / Empathy -->

<!-- ```{r child='3_ToM.Rmd'} -->
<!-- ``` -->

<!-- # Interoception -->

<!-- ```{r child='4_Intero.Rmd'} -->
<!-- ``` -->

>>>>

---
title: '**The Place of Interoception and Theory of Mind in Deception**'
subtitle: A Subtitle
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: no
    df_print: default
    code_folding: hide
    code_download: yes
  word_document:
    reference_docx: utils/Template_Word.docx
    highlight: pygments
    toc: no
    toc_depth: 3
    df_print: kable
    number_sections: yes
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '2'
    latex_engine: xelatex
editor_options:
  chunk_output_type: console
bibliography: utils/bibliography.bib
csl: utils/apa.csl
---

@@

# Manipulation Checks

```{r child='2_ManipulationChecks.Rmd'}
```

# Theory of Mind / Empathy

```{r child='3_ToM.Rmd'}
```

# Interoception

```{r child='4_Intero.Rmd'}
```
